Phenomenological Robotics

### 2011-12-02 draft.tex
Wrote on the IKEA scenario.

>>>>

\section{The IKEA scenario}

\begin{quotation}
  A hammer is for hammering.
\end{quotation}

If you have a nail nearby, that might be the case. If you are assembling IKEA
furniture outdoors, however, a hammer might as well be ``for paper weighting''.
In the same sense, a ladder is only ``for climbing'' when you have the need to
reach a high place. Most of the times, a ladder will be
``for being in the way''.

Also, screwdrivers are, supposedly, ``for driving screws''. But what happens
when you a have a flat screwdriver and need to drive a Phillips-head screw? It
is harder to drive it, but have you ever tried driving a flat head screw with a
Phillips screwdriver? It won't work, and you'll start asking yourself what is
wrong, and what you can do to fix it.

You will be having a breakdown, as described by Heidegger, and the screwdriver
will cease to be \emph{ready-to-hand} and become \emph{present-at-hand} until
you can figure out the problem. But how do we equip a robot with the same
capabilities so that it can function in a human world?
